Paper on the carbonate chemistry at Ny-Ålesund

### 2020-03-12 paper.Rmd
refined water masses chunk

```{r water masses, fig.width=15, fig.height=15, echo=FALSE, message= FALSE}
# One tries to identify water masses coming from the Atlantic or freshwater
temp_sal <- d_all %>%
  ggplot(aes(x = sal_fb, y = temp_insitu, col = month), na.rm=TRUE) +
  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
  labs(title="Temperature vs salinity SBE45",x="Salinity", y="Temp. (°C)") +
  coord_fixed() +
  Mytheme(size_labs = 8) #+
  #theme(axis.text.x=element_blank())
#  +annotation_custom(grob_A)
print(temp_sal)

>>>>

```{r water masses, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
# One tries to identify water masses coming from the Atlantic or freshwater
temp_sal <- d_all %>%
  #dplyr::mutate(month=factor(month)) %>%
  ggplot(aes(x = sal_fb, y = temp_insitu), na.rm=TRUE) +
  geom_point(aes(colour=factor(month)), na.rm=TRUE, size=size_point) + 
  labs(title="Temperature vs salinity SBE45",x="Salinity", y="Temp. (°C)") +
  facet_wrap(~ year) +
  stat_smooth(method=lm, na.rm=TRUE, show.legend=TRUE, se=FALSE, aes(fill=factor(month), colour=factor(month))) +
  coord_fixed() +
  Mytheme(size_labs = 8) 
  #scale_color_viridis(name="Month", discrete=FALSE, option="plasma")
print(temp_sal)
